When I think back to starting with the Supernova Cosmology Project
nearly six years ago, it was partially the project that convinced me
to join the group but mostly it was the enthusiasm of {\bf Saul
  Perlmutter}.  Throughout this work his unflagging determination has
been a source of inspiration. I have been thankful for the opportunity
and freedom to work on the areas of analysis I found most interesting
while still having Saul's guidance whenever I needed it. In writing
and presenting, Saul's comments have been particularly insightful
and (hopefully) have shaped the way I communicate scientifically. I
won't soon forget the long nights on the phone working on
\emph{HST} proposals!

I have {\bf Kyle Dawson} to thank for recruiting me to join the group and
for being a second advisor throughout my time here. It was also Kyle
who urged me to write up the peculiar transient SN SCP06F6 which ended
up not only being an important result from our survey but also gave me
the opportunity to gain experience talking to the media. 

Of course this work has been done as part of a larger project and
would have been impossible without the work and expertise of many
fellow group members. I can't list everything that people have done,
but I am indebted to {\bf David Rubin} for being with me from the
beginning of the supernova search, to {\bf Natalia Connolly} for all
her help on software when I was starting out, to {\bf Nao Suzuki} for
his late nights reducing ACS images, to {\bf Joshua Meyers} for all
his host galaxy analysis and for introducing me to Python for
astronomy, to {\bf Xiaosheng Huang} for his expertise in lensing, and
to {\bf Hannah Fakhouri} for careful feedback on all my work. Among
other things, I am grateful to {\bf Rahman Amanullah} for his
computing expertise, ``life advice'' and, most of all, for how he
brought the LBL SCP group together during his time in Berkeley. I
don't know exactly how he does it, but {\bf Chris Lidman}'s tireless
work on many aspects of the survey bears special mention, as does {\bf
Greg Aldering}'s observing expertise and detailed input on the
analyses presented here.  Special thanks go to {\bf Tony Spadafora}
for so many little things and for always being there to provide a
perspective.

Finally, {\bf Lauren Tompkins} has been by my side throughout my
graduate career, even when she was in a different country. Though I
sometimes like to pretend otherwise, her passion for physics has
always been inspiring. And of course, the biggest thanks go to my
family for their constant support throughout my 24 years of schooling.

\vspace{8pt}
Financial support for this work was provided by NASA through program
GO-10496 from the Space Telescope Science Institute, which is operated
by the Association of Universities for Research in Astronomy, Inc.,
under NASA contract NAS 5-26555.  This work was also supported in part
by the Director, Office of Science, Office of High Energy and Nuclear
Physics, of the U.S. Department of Energy under Contract
No. AC02-05CH11231.
